Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-06-09 WSSSPE1_report/WSSSPE1_summary_report.tex
minor wording changes in next text in S2

>>>>

The workshop received submissions from eight North
American and European countries. In some instances authors collaborated across
multiple countries towards jointly authored papers. A majority of
contributions came from the US with 42 papers where at least one author was
affiliated with a US institution. A total of 10 submissions were from 
Europe and 4 were from Canada.  This is not surprising for a workshop
being held in the US.  We believe future versions of the workshop will
have contributions from more countries and more continents.

In terms of subject of the papers, the submissions were dominated by the domain
of practice of sustainable software engineering and management with about 32
papers based on these themes. These papers were further based on a variety of
disciplines including infrastructure and architecture, user engagement, and
governance. Additionally, 18 papers were based on the sciences and
applied mathematics domains with disciplines including High Energy Physics,
Bioinformatics, Nanotechnology, Chemistry, and material sciences. Others were
included topics such as science gateways and visualization.  Again, given that
this workshop was held with a computer and computational science conference,
these numbers are not surprising.
